---
title: "eda_la1"
author: "aditya"
date: '2022-07-02'
output:
  word_document: default
  html_document: default
---

```{r}
value<-read.csv(file.choose(),sep=',',header=TRUE);
value;

```
```{r}
value; 
```
```{r}
 class(value);
```
```{r}
 value1<-as.factor(value$Country.name);
``` 
```{r}
 value1;
``` 
```{r}
 value2<-as.numeric(value1);
```
```{r}
 value2<-as.numeric(value1);
```
```{r}
 value2;
``` 
```{r}
 as.factor(value2);
```
```{r}
 value[1];
```
```{r}
 value[3];
```

```{r}
 value[1:3];
```

```{r}
 value[-1];
```

```{r}
 value[c(1,3,4,8)];
``` 

```{r}
 value[value>5];
```
```{r}
 length(value);
```

```{r}
 value[(length(value)-2):length(value)];
```
```{r}
 max(value$lowerwhisker);
```

```{r}
 max(value$Country.name);
```

```{r}
 min(value$lowerwhisker);
```

```{r}
 max(value$Regional.indicator);
```

```{r}
 which(value==max(value$Country.name));
```
```{r}
 value[seq(1,length(value),5)];
```

```{r}
 sort(value$Country.name);
```

```{r}
 sort(value$Standard.error.of.ladder.score);
```
```{r}
 sort(value$Social.support);
```
```{r}
 order(value$Country.name); 
```
```{r}
 order(value$Standard.error.of.ladder.score);
```
```{r}
 sort(value$Social.support);
```
```{r}
 rank(value$Country.name);
```

```{r}
 rank(value$Standard.error.of.ladder.score);
```
```{r}
 rank(value$Social.support);
```
```{r}
 value[3,3];
```

```{r}
 value[3,1:4];
```

```{r}
 value[,3];
```

```{r}
 value[c(1,3,5,7),-4];
```

```{r}
 value[c(1,3,5,7),"Social.support"];
```

```{r}
 value[3];
```

```{r}
 value[c(1,100),];
```

```{r}
 order(value$upperwhisker,value[,2]);
```
```{r}
 summary(value);
```

```{r}
 str(value);
``` 
```{r}
 with(value,order(value$upperwhisker,value$Social.support));
```

```{r}
 value$lowerwhisker;
```

```{r}
 value$Regional.indicator;
```

```{r}
 value$Regional.indicator[1:4];
```

```{r}
 value[,'Regional.indicator'];
```

```{r}
 search();
```

```{r}
 with(value,Regional.indicator);
```

```{r}
 with(value,upperwhisker);
```

```{r}
head(value);
```

```{r}
 tail(value);
```

```{r}
head(value,n=10);
```
```{r}
 summary(value);
```
```{r}
 names(value)
```

```{r}
 row.names(value);
```

```{r}
 colnames(value);
```

```{r}
 dimnames(value);
```

```{r}
 value4.mat=as.matrix(value);
value4.mat;
```

```{r}
 value5.list=as.list(value);
value5.list;
```

```{r}
 mean(value$upperwhisker);
```

```{r}
 mean(value$Ladder.score);
```

```{r}
 min(value$upperwhisker);
```

```{r}
 min(value$Ladder.score);
```

```{r}
 max(value$upperwhisker);
```

```{r}
 max(value$Ladder.score);
```

```{r}
 length(value$upperwhisker);
```

```{r}
 sd(value$upperwhisker);
```

```{r}
 sd(value$Ladder.score);
```

```{r}
 log(value$Ladder.score);
```

```{r}
 quantile(value$Ladder.score);
```

```{r}
 fivenum(value$Ladder.score);
```

```{r}
 quantile(value$Ladder.score,0.2);

```{r}
 quantile(value$Ladder.score,c(0.2,0.5,0.8));
```

```{r}
 quantile(value$Ladder.score,c(0.5,0.75,0.25));
```

```{r}
 cumsum(value$Ladder.score);
```

```{r}
 cummax(value$Ladder.score);
```

```{r}
 cummin(value$Ladder.score);
```

```{r}
 cumprod(value$Ladder.score);
```

```{r}
 seq(along=value);
```
```{r}
 seq_along(value);
```
```{r}
 seq(from=1,to=10,by=2);
```

```{r}
 library(dplyr);
value %>% mutate(newcol=1);
```

```{r}
 value %>% select(-Logged.GDP.per.capita);
```

```{r}
 value %>% select(Ladder.score,everything());
```

```{r}
value %>% filter(Country.name=="New Zealand" & Ladder.score>=6.965 &
Ladder.score<=7.277);
```

```{r}
value %>% filter(Country.name=="New Zealand" & Ladder.score>=6.965 &
Ladder.score<=7.277) %>% select(Country.name,Ladder.score);
```

```{r}
value %>% rename(Country=Country.name);
```

```{r}
with(value,table(upperwhisker,Ladder.score));
```


```{r}
library(ggplot2);
ggplot(value,aes(x=Ladder.score, y=upperwhisker))+geom_point();
```

```{r}
ggplot(value,aes(x=Ladder.score, y=upperwhisker))+geom_point();
```
```{r}
library(dplyr);
vec<-rep(c(2),149);
value %>% mutate(newcol1=vec);
```
```{r}
library(ggplot2);
ggplot(value,aes(x=Ladder.score, y=upperwhisker))+geom_line();
```

```{r}
ggplot(value,aes(x=Ladder.score, y=upperwhisker))+geom_line()+geom_point();
```

```{r}
ggplot(value,aes(x=Ladder.score, y=upperwhisker))+geom_col();
```

```{r}
ggplot(value,aes(x=Ladder.score))+geom_bar();
```

```{r}
ggplot(value,aes(x=Ladder.score))+geom_histogram();
```

```{r}
ggplot(value,aes(x=Ladder.score))+geom_histogram(binwidth=4);
```
```{r}
ggplot(value,aes(x=Ladder.score, y=upperwhisker))+geom_boxplot();
```


