---
title: "EDA_LA2"
author: "Aditya A V S"
date: '2022-07-04'
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}

data<-read.csv("C:/Users/anany/Downloads/world-happiness-report-2021.csv",header=TRUE,sep=',')
```
```{r}

data
```
```{r}
colnames(data)
```
scatter plot plotted for n_student in x axis and pretest in y axis
```{r}
library(ggplot2)
plot(data$Ladder.score,data$lowerwhisker)
```
Visualizing the scatter plot using ggplot() function
```{r}
ggplot(data,aes(x=Ladder.score,y=upperwhisker))+geom_point()
```

Visualizing the scatter plot using ggplot() function when x and y values are vectors
```{r}
ggplot(NULL,aes(x=data$Ladder.score,y=data$Social.support))+geom_point()
```

Visualizing the line graph using plot function by passing x and y parameters
```{r}
plot(data$Ladder.score,data$Social.support,type="l");
```



Visualizing the line graph using the ggplot() function
```{r}
ggplot(data,aes(x=lowerwhisker,y=upperwhisker)) + geom_line()
```
Visualizing the line graph using geom_line() function and plotting the points on top of it
```{r}
ggplot(data,aes(x=upperwhisker,y=lowerwhisker)) + geom_line()+geom_point()
```

Visualizing the bar graph by plotting x and y axis using barplot function
```{r}
barplot(data$Ladder.score,names.arg=data$lowerwhisker)
```

Visualizing the bargraph using ggplot() function
```{r}
ggplot(data,aes(x=lowerwhisker,y=upperwhisker))+geom_col()
```

Visualizing the bargraph using ggplot() function using geom_bar() function
```{r}
ggplot(data,aes(x=lowerwhisker))+geom_bar()
```

Visualizing the histograms using the hist() function
```{r}
hist(data$Ladder.score,breaks=10)
```
Visualizing the histograms using the ggplot() function
```{r}
ggplot(data,aes(x=Ladder.score)) + geom_histogram(binwidth = 4)
```

Visualizing the bargraph using ggplot() function and it fills the light blue colour to the bars and the border lines of the bar will be black
```{r}
ggplot(data,aes(x=Ladder.score,y=data$lowerwhisker)) + geom_col(fill="lightblue",colour="black")
```
Visualizing the bargraph and mapping the posttest coloumn to the fill colour
```{r}
ggplot(data,aes(x=Ladder.score,y=lowerwhisker,fill=upperwhisker))+geom_col(position="dodge")
```


Bar of points
```{r}
ggplot(data,aes(x=Ladder.score))+geom_bar()


```

Creating a boxplot using boxplot() function
```{r}
plot(data$Ladder.score, data$lowerwhisker)

```

Put interaction of two variables on x-axis
```{r}
boxplot(Ladder.score ~  + lowerwhisker, data = data)
```

Visualization of boxplot using the ggplot() function
```{r}
ggplot(data, aes(x = upperwhisker, y = Ladder.score)) + geom_boxplot()

```

Make box plots for multiple variables, by combining the variables
with interaction(),
```{r}
ggplot(data, aes(x = interaction(lowerwhisker, Ladder.score), y = upperwhisker)) + geom_boxplot()

```

When the x variable is a factor, you must also use aes(group=1) to
ensure that ggplot knows that the data points belong together and should be connected with a line
```{r}
ggplot(data, aes(x = upperwhisker, y = lowerwhisker, group = 1)) + geom_line()
```

Variables mapped to the x- and y-axes, map another (discrete) vari‐
able to colour or linetype
```{r}
ggplot(data, aes(x = upperwhisker, y = lowerwhisker, colour = "red")) + geom_line()


```


Changing the appearnce of the lines
```{r}
ggplot(data, aes(x = lowerwhisker, y = upperwhisker)) +
 geom_line(linetype = "dashed", size = 1, colour = "blue")
```

In geom_point(), set the size, shape, colour, and/or fill outside of aes() (the
result is shown
```{r}
ggplot(data, aes(x = upperwhisker, y = lowerwhisker)) + geom_line() +
 geom_point(size = 4, shape = 22, colour = "darkred", fill = "pink")
```

 Visualizing the density curve using geom_density() fucntion and map a continuous variable n_student to x
```{r}
ggplot(data, aes(x = lowerwhisker)) +
 geom_density()
```

It removes the lines along the bottom and side and using expand_limits() increases the y range to include the value 0
```{r}
ggplot(data, aes(x =Ladder.score)) + geom_line(stat = "density") +
 expand_limits(y = 0)

```

Visualizing the density curve using the geom_line function and using a adjust parameter which is used to get the extent to which the density curve should be smoother
```{r}
ggplot(data, aes(x = lowerwhisker)) +
 geom_line(stat = "density") +
 geom_line(stat = "density", adjust = .25, colour = "red") +
 geom_line(stat = "density", adjust = 2, colour = "blue")
```


Visualizing the frequency polygon
```{r}
ggplot(data, aes(x=Ladder.score)) +  geom_freqpoly()


```

Visualizing the frequency polygon along with the bandwidth parameter
```{r}
ggplot(data, aes(x = upperwhisker)) +  geom_freqpoly(binwidth = 4)

```

Visualization of the boxplot by changing the width of the bars
```{r}
ggplot(data, aes(x = factor(Ladder.score), y = upperwhisker)) + geom_boxplot(width = .5)
```

Visualization of the a box plot of just a single group, we have to provide some arbitrary value for x.In this case,we’ll set it to 1 and remove the x-axis tick markers and label
```{r}
ggplot(data, aes(x = 1, y = Ladder.score)) +
 geom_boxplot() +
 scale_x_continuous(breaks = NULL) +
 theme(axis.title.x = element_blank())

```


Adding the notches to the box plot using  geom_boxplot() and set notch = TRUE
```{r}
ggplot(data, aes(x = factor(lowerwhisker), y = upperwhisker)) +
 geom_boxplot(notch = TRUE)
```

Visualizing the box plot by adding the stat_summary function which includes the function of mean which leads to adding of the means to the boxplot
```{r}
ggplot(data, aes(x = factor(lowerwhisker), y = upperwhisker)) +
 geom_boxplot() +
 stat_summary(fun.y = "mean", geom = "point", shape = 23, size = 3,
 fill = "white")
```

Visualization of the violin plot 
```{r}
 ggplot(data, aes(x = Ladder.score, y = lowerwhisker)) + geom_violin()
```

Visualization of the violin plot with the boxplpot overlaid on it
```{r}

ggplot(data,aes(x=lowerwhisker,y=upperwhisker))+ geom_violin() +
 geom_boxplot(width = .1, fill = "black", outlier.colour = NA) +
 stat_summary(fun.y = median, geom = "point", fill = "white", shape = 21,
 size = 2.5)
```


Visualization of the violin plot by adding tails at the end
```{r}
ggplot(data,aes(x=Ladder.score,y=lowerwhisker))+ geom_violin(trim = FALSE)

```

Visualization  of the violin plot with area proportional to number of observations
```{r}
 ggplot(data,aes(x=lowerwhisker,y=Ladder.score)) + geom_violin(scale = "count")
```

Visualization of the dot plot using the geom_dotplot() function
```{r}
ggplot(data, aes(x = Ladder.score)) +
 geom_dotplot()
```

Visualization of dot plot using geom_dotplot() bins the data along the x-axis and stacks on the y-axis
```{r}
 ggplot(data,aes(x=upperwhisker)) +
 geom_dotplot(binwidth = .25) +
 geom_rug() +
 scale_y_continuous(breaks = NULL) +
 theme(axis.title.y = element_blank())
```

Visualization of dot plot using dotplot() function and to use bins that are arranged with a fixed, regular spacing, like a histogram.
```{r}
 ggplot(data,aes(x=Ladder.score)) +
 geom_dotplot(method = "histodot", binwidth = .25) +
 geom_rug() +
 scale_y_continuous(breaks = NULL) +
 theme(axis.title.y = element_blank())
```
Visualization of dot plot and the dots can also be stacked centered using stackdir="center"
```{r}
 ggplot(data,aes(x=lowerwhisker))+
 geom_dotplot(binwidth = .25, stackdir = "center") +
 scale_y_continuous(breaks = NULL) +
 theme(axis.title.y = element_blank())
```
Visualization of dot plot and the dots can also be stacked centered using stackdir="centerwhole"
```{r}
  ggplot(data,aes(x=upperwhisker)) +
 geom_dotplot(binwidth = .25, stackdir = "centerwhole") +
 scale_y_continuous(breaks = NULL) +
 theme(axis.title.y = element_blank())
```
Visualization of dotplot and to stack the dots along the y-axis, and group
them along the x-axis, by setting binaxis = "y".
```{r}
ggplot(data, aes(x = Ladder.score, y = upperwhisker)) +
 geom_dotplot(binaxis = "y", binwidth = .5, stackdir = "center")
```
Visualization of dot plots overlaid on box plots and to make the dots hollow and have the box plots not show outliers
```{r}
ggplot(data, aes(x = lowerwhisker, y = upperwhisker)) +
 geom_boxplot(outlier.colour = NA, width = .4) +
 geom_dotplot(binaxis = "y", binwidth = .5, stackdir = "center", fill = NA)
```
Visualization of dot plot on top of box plot by specifying binaxis,binwidth,stackdir 
```{r}
ggplot(data, aes(x = upperwhisker, y = lowerwhisker)) +
 geom_boxplot(aes(x = as.numeric(upperwhisker) + .2, group = lowerwhisker), width = .25) +
 geom_dotplot(
 aes(x = as.numeric(upperwhisker) - .2, group = upperwhisker),
 binaxis = "y",
 binwidth = .5,
 stackdir = "center"
 ) +
 scale_x_continuous(
 breaks = 1:nlevels(data$lowerwhisker),
 labels = levels(data$Ladder.score)
 )
```
 Plotting the density of two-dimensional data
```{r}
 ggplot(data,aes(x=Ladder.score,y=lowerwhisker)) +
 geom_point() +
 stat_density2d()
```
Maps the height of the density curve to the color of the contour lines, by using ..level..
 
```{r}
ggplot(data,aes(x=upperwhisker,y=lowerwhisker))+
 stat_density2d(aes(colour = ..level..))
```
Maps density estimate to fill color
```{r}
ggplot(data,aes(x=lowerwhisker,y=Ladder.score)) +
 stat_density2d(aes(fill = ..density..), geom = "raster", contour = FALSE)
```
With points, and map density estimate to alpha
```{r}
 ggplot(data,aes(x=Ladder.score,y=lowerwhisker)) +
 geom_point() +
 stat_density2d(aes(alpha = ..density..), geom = "tile", contour = FALSE)
```

